### 2025-05-07 data/README.Rmd
Add hoaddata indicators
Improve data documentation

This folder contains analytical datasets providing aggregated counts on the uptake of open access in hybrid journals included in transformative agreements by journal and country information between 2019 and 2023. A particular focus was on whether publications were from eligible authors who could use such agreements. For this purpose, the affiliations of  first and corresponding authors were analysed.

@@

>>>>

This folder contains analytical datasets providing aggregated counts from proprietary bibliometric databases on the uptake of open access in hybrid journals included in transformative agreements by journal and country information between 2019 and 2023. A particular focus was on whether publications were from eligible authors who could use such agreements. For this purpose, the affiliations of  first and corresponding authors were analysed.

@@

The folder also include respective datasets derived from the openly available hoaddata (`hoad`), v.0.3. It combines data from several open metadata sources, including cOAlition S Public Transformative Agreement Data powering the Journal Checker Tool, Crossref and OpenAlex. <https://github.com/subugoe/hoaddata/releases/tag/v.0.3>. Note that the OA indicators were calculated for first authors only.
